---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# QGERT

<!-- badges: start -->
<!-- badges: end -->

QGERT stands for Qualitas Genetic Evaluation Routine Tools. The goal of QGERT is to provide a set of standardized tools to prepare data and topost-process results of the routine genetic evaluation. The main focus of the post-processing is on quality assurance and on results checking. As a consequence of that, principles of reproducibility of all tasks are followed as closely as possible.


## Installation

Because the package is only useful in the context of the genetic evaluations done at [Qualitas AG](https://qualitasag.ch), the package will not be released to CRAN. The development version can be installed from [GitHub](https://github.com/) with:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("pvrqualitasag/qgert")
```


## Example

Examples of basic use cases are shown in the different articles that are available from this site. A short description of all available articles is listed below.

* Getting Started: Description of basic usage of the functionality provided by `qgert`.
* Comparison Plots: Explanation of what a comparison plot is.
* Comparison Plot Report: Combination of comparison plots in a single report.
* Spinning bash script: Conversion of specially annotated bash scripts into an html page.


