---
title: "Generate Comparison Plot Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generate Comparison Plot Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(qgert)
```


## Disclaimer
The definition of a `comparison plot report` and how such reports are generated is described in this vignette.


## Terminology
A comparison plot report is a document that shows a series of comparison plots arranged in two columns from two subsequent routine evaluations. Please have a look at the separate article on [comparison plots](https://pvrqualitasag.github.io/qgert/articles/comparison_plots.html) to find how these plots are defined an how they are produced.


## Comparison Plot Report
Comparison plots are done during each routine evaluation for every block of traits. These plots by themselves are only meaningful with a lot of expertise and experience. But when comparing the same plot to the version that was produced during the previous evaluation, then the quality of the plot can be assessed qualitatively in the sense that it is possible to say, whether the characteristics of the current evaluation represented by a specific comparison plot are better compared to the same characteristics from the previous evaluation.

As a consequence of that the comparison of two plots of the same characteristics from two subsequent routine evaluations provides important information. Therefore the arrangement of two plots of the same characteristics from two subsequent routine evaluations next to each other in two columns makes the comparison seamless and efficient.


## Example

