---
title: "Generate Comparison Plot Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generate Comparison Plot Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(qgert)
```


## Disclaimer
The definition of a `comparison plot report` and how such reports are generated is described in this vignette.


## Terminology
A comparison plot report is a document that shows a series of comparison plots arranged in two columns from two subsequent routine evaluations. Please have a look at the separate article on [comparison plots](https://pvrqualitasag.github.io/qgert/articles/comparison_plots.html) to find how these plots are defined an how they are produced.


## Comparison Plot Report
Comparison plots are done during each routine evaluation for every block of traits. These plots by themselves are only meaningful with a lot of expertise and experience. But when comparing the same plot to the version that was produced during the previous evaluation, then the quality of the plot can be assessed qualitatively in the sense that it is possible to say, whether the characteristics of the current evaluation represented by a specific comparison plot are better compared to the same characteristics from the previous evaluation.

As a consequence of that the comparison of two plots of the same characteristics from two subsequent routine evaluations provides important information. Therefore the arrangement of two plots of the same characteristics from two subsequent routine evaluations next to each other in two columns makes the comparison seamless and efficient.


## Example
Comparison plot reports can either be generated by calling the R-wrapper function for each trait group. Using the fertility trait group as an example, the abbreviation is `fbk` and the corresponding R wrapper function is 

```{r, eval=FALSE}
qgert::create_ge_compare_plot_report_fbk(pn_cur_ge_label = 1912, pn_prev_ge_label = 1908)
```

The above function call creates the comparison plot reports for trait group `fbk`.

The same comparison plot report can be genrated using the shell script called `create_comp_plot_report_fbk.sh`. After changing to the evaluation directory, the call to the shell script shown below produces the comparison plot report.

```{bash, eval=FALSE}
cd /qualstorzws01/data_zws/fbk
./prog/create_comp_plot_report_fbk.sh -c 1912 -p 1908
```

For trait groups other than `fbk` there are analogous R wrapper functions and corresponding bash scripts.


## Updates
Whenever a new version of the comparison plot report creation pipeline is released, two steps must be performed. 

1. Update the R-package `qgert` using `devtools::install_github("pvrqualitasag/qgert")` and 
2. Updating the bash scripts using the following statement

```{bash, eval=FALSE}
cd /qualstorzws01/data_zws/fbk
/home/zws/lib/R/library/qgert/bash/install_script.sh -s /home/zws/lib/R/library/qgert/bash/create_comp_plot_report_fbk.sh -t prog
```

The above statement updates the bash script `create_comp_plot_report_fbk.sh` in subdirectory `prog` for the trait group `fbk`. 



