---
title: "Toplists of Bulls for BVCH"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Toplists of Bulls for BVCH}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qgert)
```


## Disclaimer
The features to create toplists of bulls for BVCH are described here. Originally these features were included in a RStudio-project called 'toplistbvch'. 


## Terminology
Toplists of bulls are rankings of bulls according to the predicted breeding values in different traits. The lists are exported from the database and are entered into an excel spreadsheet. The ranking of the bulls for a certain trait is entered in a different workbook. The ranking lists for the two subgroups 'BV' and 'OB' are separated by a few empty lines in the same workbook. 


## Input
The input consists of the lists of predicted breeding values for all bulls. These lists come as csv-files and they are in two different files for 'BV' and 'OB'. 


## Procedure
The procedure to create the Toplists is done according to the following steps.


1. 
