---
title: "Split gsRuns According To Predicted Runtimes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Split gsRuns According To Predicted Runtimes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qgert)
```

## Usage
The split of the gsRuns can be done using the following shell script

```{bash, eval=FALSE}
cd /qualstorzws01/data_zws/gs
./prog/split_gsRuns_sorted_rt.sh -g work/gsRuns.txt -d 1908 -m first -n 100
```

This uses the gsRuns-list stored under `work/gsRuns.txt`, it takes the runtime information from the logfiles of the archive of the 1908 evaluation and it produces 100 small job files.


## Update and Installation
This script can only be used if the R-package `qgert` is installed. On the ZWS-servers this is the case. An update of the package can be done with

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("pvrqualitasag/qgert")
```

Then the bash script `split_gsRuns_sorted_rt.sh` must be installed into the subdirectory `prog` of the GS-evaluation directory

```{bash, eval=FALSE}
/home/zws/lib/R/library/qgert/bash/install_script.sh -s ~/lib/R/library/qgert/bash/split_gsRuns_sorted_rt.sh -t /qualstorzws01/data_zws/gs/prog
```



## Purpose - Why This Is Done
Estimation of marker effects and reliability prediction is a resource intensive step during the routine genetic evaluation. Hence all these estimation tasks must be parallelized. Given a list (gsRuns-list) of computation jobs which consist of combinations of breeds, evaluation type, trait and parameter type, this list is to be split into a number of smaller lists. 

As an additional requirement, the produced number of lists should contain the jobs sorted according to their predicted running time from a previous evaluation.


## Description - How This Is Done
Given a directory where the logfiles of the previous evaluation is archived (or just a simple run-label such as 1908), the logfiles are searched for the predicted running time of the respective estimation job. This information is written to an outputfile. The outputfile is read into R where the records are sorted according to their running times. After the sort, a specified number of job-files is written. These files have the name-prefix `gsSortedRuns.txt` followed by a number. 

To prepare the binary version of the SNP-Data one gsRun-job per breed is written to the file `gsRuns.txt.snpBin`. The jobs that are contained in `gsRuns.txt.snpBin` are not contained in the `gsSortedRuns.txt`-files. Hence all the programs with partitioned gs-Runs-lists, `gsRuns.txt.snpBin` must also be used as an argument.


